---
title: "steak_survey"
author: "60070016, 60070034"
date: "April 17, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# รายงานเรื่อง ความนิยมสเต็กในแต่ละระดับความสุก

***
### ชื่อ: ไชยพงษ์ นิธิพีรวัฒน์, ธิรดา ธีร์ธรรม
### รหัสนักศึกษา: 60070016, 60070034
### เวลาเรียน: อังคาร 9.00-12.00 น.
***

## โจทย์ปัญหา :
### ปัจจัยต่าง ๆ ส่งผลต่อการเลือกรับประทานสเต็กอย่างไร ?
#### ชุดข้อมูลที่ใช้จาก fivethirtyeight : steak_survey
Data set from <https://github.com/fivethirtyeight/data/tree/master/steak-survey> by Walt Hickey

### 1. Load libraries

```{r}
library(fivethirtyeight)
library(tidyverse)

```

### 2. Look at the data (steak_survey) 

```{r}
# print out the dataframe
steak_survey

# Approximately look
summary(steak_survey)
```

### 3. Looking for answers

```{r}
#Find percent of each steak prepared's type
new_df <- steak_survey %>%
            filter(steak_prep != "NA") %>%
            group_by(steak_prep) %>%
            summarise(amount= n()) %>%
            mutate(percent = amount/sum(amount))
            
new_df

#Separate amount of smoker in each steak prepared's type
smoke_df <- steak_survey %>%
            filter(steak_prep != "NA", smoke != "NA") %>%
            group_by(smoke, steak_prep) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))

smoke_df

#Separate amount of drinker in each steak prepared's type
alco_df <- steak_survey %>%
            filter(steak_prep != "NA", alcohol != "NA") %>%
            group_by(alcohol, steak_prep) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))

alco_df

#Separate sex in each steak prepared's type
sex_df <- steak_survey %>%
            filter(steak_prep != "NA") %>%
            group_by(female, steak_prep) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))

sex_df

#Separate by age
age_df <- steak_survey %>%
            filter(steak_prep != "NA", age != "NA") %>%
            group_by(age, steak_prep) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))
age_df

#Separate by household income
hhold_df <- steak_survey %>%
            filter(steak_prep != "NA") %>%
            group_by(hhold_income, steak_prep) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))
hhold_df

#Separate by education
educate_df <- steak_survey %>%
            filter(steak_prep != "NA", educ != "NA") %>%
            group_by(educ, steak_prep, educ) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))
educate_df

#Separate by region
region_df <- steak_survey %>%
            filter(steak_prep != "NA", region != "NA") %>%
            group_by(region, steak_prep) %>%
            summarise(amount=n()) %>%
            mutate(percent = amount/sum(amount))

region_df
```

### 4. Visualize data

```{r}
#Plot steak prepared chart
b0 <- ggplot(new_df, aes(x = steak_prep)) +
        # add geometry of the plot (bar chart)
        #colour CR.https://ggplot2.tidyverse.org/reference/aes_colour_fill_alpha.html
        geom_bar(aes(y = percent*100), stat = "identity", fill = "pink") +
        # add labels
        labs(x="Steak Prepared", y="Percent", title="Steak Prepared Chart") +
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0)
        
b0 + coord_flip()
```



```{r}
#Plot bar chart of smoker's steak
b1 <- ggplot(smoke_df, aes(x = steak_prep, fill = smoke)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts CR.https://sebastiansauer.github.io/percentage_plot_ggplot2_V2/
        facet_grid(~smoke) +
        # add labels
        labs(x="Smoker's Steak Prepared", y="Percent", title="Smoker's Steak Prepared Bar Chart") +  
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart CR.https://stackoverflow.com/questions/1330989/rotating-and-spacing-axis-labels-in-ggplot2
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b1 + coord_flip()
```

```{r}
#Plot bar chart of drinker's steak
b2 <- ggplot(alco_df, aes(x = steak_prep, fill = alcohol)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts
        facet_grid(~alcohol) +
        # add labels
        labs(x="Drinker's Steak Prepared", y="Percent", title="Drinker's Steak Prepared Bar Chart") +
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b2 + coord_flip()
```

```{r}
#Plot bar chart of each sex's steak
b3 <- ggplot(sex_df, aes(x = steak_prep, fill = female)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts
        facet_grid(~female) +
        # add labels
        labs(x="Each sex's Steak Prepared", y="Percent", title="Each sex's Steak Prepared Bar Chart") +  
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b3 + coord_flip()
```

```{r}
#Plot bar chart of each age's steak
b4 <- ggplot(age_df, aes(x = steak_prep, fill = age)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts
        facet_grid(~age) +
        # add label
        labs(x="Each Span Of Age's Steak Prepared", y="Percent", title="Each Span Of Age's Steak Prepared Bar Chart")+  
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b4 + coord_flip()
```


```{r}
#Plot bar chart of household income's steak
b5 <- ggplot(hhold_df, aes(x = steak_prep, fill = hhold_income)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts
        facet_grid(hhold_income~.) + 
        # add labels
        labs(x="Household Income Range's Steak Prepared", y="Percent", title="Household Income Range's Steak Prepared Bar Chart") +  
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b5 + coord_flip()
```


```{r}
#Plot bar chart of education's steak
b6 <- ggplot(educate_df, aes(x = steak_prep, fill = educ)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts
        facet_grid(educ~.) + 
        # add labels
        labs(x="Education in Steak Prepared", y="Percent", title="Education's Steak Prepared Bar Chart") +  
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b6 + coord_flip()
```


```{r}
#Plot bar chart of region's steak
b7 <- ggplot(region_df, aes(x = steak_prep, fill = region)) +
        # add geometry of the plot (bar chart)
        geom_bar(aes(y = percent*100), stat = "identity") +
        #Separate charts
        facet_grid(region~.) + 
        # add labels
        labs(x="Region in Steak Prepared", y="Percent", title="Region's Steak Prepared Bar Chart") +  
        geom_text(aes(label = scales::percent(percent), y = percent*100), stat= "identity", vjust = 0) +
        #Rotate text under the chart
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .35))

b7 + coord_flip()
```

***
#สรุปผล:
###1. จากกราฟ จะเห็นได้ว่า ลำดับความนิยม ของประเภทของ steak จะเป็น Medium rare, Medium, Medium well, Well, Rare ตามลำดับจากมากไปน้อย
```{r}
b0 + coord_flip()
```

###2. จะเห็นได้ว่า กราฟผู้ที่สูบบุหรี่และดื่มสุรา มีรูปแบบกราฟที่เหมือนกับกราฟรวม จึงคาดการว่า การสูบบุหรี่และดื่มสุราไม่มีผล หรือมีผลน้อยต่อการเลือกทาน steak
```{r}
b1 + coord_flip()
b2 + coord_flip()
```

###3. ส่วนเพศนั้นไม่มีผลต่อความนิยม steak ในระดับต่าง ๆ
```{r}
b3 + coord_flip()
```

###4. ในช่วงอายุ 18 - 29 ปีจะนิยม steak ระดับ Medium มากกว่า Medium rare
###ส่วนในช่วงอายุ มากกว่า 60 ปี จะนิยม steak ระดับ Rare มากกว่า Well
```{r}
b4 + coord_flip()
```

###5. คนที่มีรายได้ครัวเรือนมากกว่า 150,000 ดอลลาร์ มีแนวโน้มว่านิยม steak ระดับ Medium มากกว่า Medium rare
```{r}
b5 + coord_flip()
```

###6. คนที่จบการศึกษาระดับบัณฑิตศึกษามีแนวโน้มที่จะนิยม steak ระดับ Rare มากกว่า Well
```{r}
b6 + coord_flip()
```

###7. คนที่อยู่ ใน Middle Atlantic จะนิยม steak ระดับ Medium มากกว่า Medium rare เล็กน้อย
###คนที่อยู่ใน East South Central, Mountain และ West South Central จะไม่นิยมทาน steak ระดับ Rare 
```{r}
b7 + coord_flip()
```
***